signalHsmm - a novel semi-Markov model of eukaryotic signal peptides

### 2015-06-18 paper.tex
updated code and dataset in fasta file

The best and the worst encoding share some similarities. The both groupings have strongly pronounced highly hydrophobic group 3 (see Table~\ref{tab:best}, Table~\ref{tab:best} and Figure~\ref{fig:enccomp}.

>>>>

The best and the worst encoding share some similarities. In both cases Group 1 tends to contain polar

The both groupings have strongly pronounced non-polar and highly hydrophobic group 3 (see Table~\ref{tab:best}, Table~\ref{tab:best} and Figure~\ref{fig:enccomp}) containing isoleucine, leucine, methionine and valine.
